Liptschiz

### 2024-02-23 lipschitz/valabstraction.tex
pptx

The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$

We can use the following extra constraints (besides 4 constraints about $\hat{x}_i'=\ReLU(x_i')$) to build this relation:\begin{align*}
	&\hat{y}_i \geq -\hat{x}'_i \hspace*{1ex} \wedge \hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+a\beta_i  \hspace*{1ex}\wedge\hspace*{1ex} x_i'+y_i \leq a\beta_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \geq (1-a)\alpha_i \\
	&\hat{y}_i \geq -\hat{x}'_i+(x_i'+y_i) \hspace*{1ex}\wedge\hspace*{1ex} \hat{y}_i \leq -\hat{x}'_i+(x_i'+y_i) +(1-a)\alpha_i \\
	& x_i'+y_i \geq \alpha_i \hspace*{1ex}\wedge\hspace*{1ex}  x_i'+y_i \leq \beta_i
\end{align*}And its plots is as follows:

\hspace*{-10ex}
\begin{tikzpicture}
	\begin{axis}[	axis on top, xlabel = \(x'_i\),
		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
				set layers=default,
	xmax = 4, xmin = -4,
ymax = 1, ymin = -1,		
zmax = 1, zmin = -1,
				unit vector ratio=1 1 1, scale=3,
				view={60}{50}, ytick   = {-1,0,1},
				yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
				xticklabels = {$0$}, ztick   = {-1,0,1},
				zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
				]
		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

@@

>>>>

The relation between $y_i$, $x'_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i).$ And its plots is as follows:

\iffalse
\hspace*{-10ex}
\begin{tikzpicture}
	\begin{axis}[	axis on top, xlabel = \(x'_i\),
		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
				set layers=default,
	xmax = 4, xmin = -4,
ymax = 1, ymin = -1,		
zmax = 1, zmin = -1,
				unit vector ratio=1 1 1, scale=3,
				view={60}{50}, ytick   = {-1,0,1},
				yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
				xticklabels = {$0$}, ztick   = {-1,0,1},
				zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
				]
		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

@@

	\end{axis}
\end{tikzpicture}
\fi
